\begin{problem}{A Menace 2 \$ociety}{standard input}{standard output}{15 seconds}{256 megabytes}

Jay and Jay's son ja\$on are playing a game together. This game involves counting
occurrences of a string $J$ in another string $S$. But, ja\$on has
gotten so good at this game, Jay is at a loss for how to keep it interesting.

Jay is a menace to society and has decided to make the game more fun for Jay's
son ja\$on by adding some new rules. On top of $S$, Jay will define $K + 1$ more strings
$S_0, S_1, \dots, S_K$. $S_i$ can be created by taking the first character in $S$, skipping the next $i$ characters, then taking the next character, then skipping the next $i$ characters, and so on. For example, if $S$ is \texttt{southpacific}, then $S_2$ is \texttt{staf}. Note that $S_0$ and $S$ are the same string.

Further, in honour of Jay's son ja\$on's name, Jay will use letters from a language called `Engli\$h', which contains all lowercase English letters, except that the letter \texttt{s} is replaced with the letter \texttt{\$}. So \texttt{\$outh}, \texttt{pacific}, \texttt{programming}, \texttt{conte\$t} are valid words in Engli\$h, but \texttt{south} and \texttt{contest} are not.

In Jay's new game, he must find the string $J$ in each of the $K+1$ words.
For example, if $S$ is \texttt{aacbc} and $J$ is \texttt{ac}, then $S_1$ is \texttt{acc}, and $S_2$ is \texttt{ab}. $J$ is found once in both $S_0$ and $S_1$, but not $S_2$.

Given the strings $S$ and $J$, as well as the value of $K$, determine the number of occurrences of $J$ in each $S_i$.


\InputFile
The first line of the input contains a single integer $K$~($0 \leq K < 1\,000\,000$),
which is the number of strings to check.

The second line of the input contains a single non-empty string $S$ that has strictly more than $K$ and at most $1\,000\,000$ characters, consisting of Engli\$h letters.

The third line of the input contains a single non-empty string $J$, consisting of Engli\$h letters. The length of $J$ is at most the length of $S$.


\OutputFile
Display the number of occurrences of $J$ in $S_0, S_1, \dots, S_K$.

\Examples

\begin{example}
\exmpfile{example.01}{example.01.a}%
\exmpfile{example.02}{example.02.a}%
\exmpfile{example.03}{example.03.a}%
\exmpfile{example.04}{example.04.a}%
\end{example}

\end{problem}

